From Education to Entrepreneurship

### 2014-12-12 index.Rmd
Theme attempt

---
title: 'From Education to Entrepreneurship'
author: "Sam Dundon and Thierry Racaud"
date: "December 6, 2014"
output: html_document
---

@@

>>>>

---
title: 'From Education to Entrepreneurship'
author: "Sam Dundon and Thierry Racaud"
date: "December 6, 2014"
output: html_document
theme: Cosmo
---

@@

### More information

For more information about our project, including an academic paper on the topic, please see our [GitHub repository](https://github.com/SamDund/Assign2Education)
